---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## readwriteaws

<!-- badges: start -->
  [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Overview

This package is designed for Poisson employees to easily access our files within our AWS s3 buckets. The general workflow for this package is:  
1. Get the list of files   
2. Download them to your local drive  
3. Use them as normal  

## Installation

To install the latest version from [GitHub](https://github.com/poissonconsulting/usepois)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/readwriteaws")
```

## Examples



## How to Contribute

Please report any [issues](https://github.com/poissonconsulting/readwriteaws/issues).

[Pull requests](https://github.com/poissonconsulting/readwriteaws/pulls) are always welcome.

Please note that the readwriteaws project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
