---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## readwriteaws

<!-- badges: start -->
  [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Overview

This package is designed for Poisson employees to easily access our files within our AWS s3 buckets. The general workflow for this package is:  
1. Get the list of files   
2. Download them to your local drive  
3. Use them as normal  

## Installation

To install the latest version from [GitHub](https://github.com/poissonconsulting/usepois)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/readwriteaws")
```

## Credentials

Credentials need to be set up properly so you have permission to access AWS.
It is recommended to put the credentials in your .Renviron file.
The names of the variables must match below or you will not be authenticated.

```
AWS_ACCESS_KEY_ID=GET_FROM_AWS_USER
AWS_SECRET_ACCESS_KEY=GET_FROM_AWS_USER
AWS_REGION=ca-central-1
```

Credentials can also be passed to the functions directly. See examples for more info. 

## Examples

#### Downloading files for analysis
```{R, eval = FALSE}
capture_2021 <- rwa_list_su_files(bucket_name = "purple-lake-poissonconsulting", 
                                  data_type = "punch-data",
                                  year = 2021,
                                  file_extension = "csv")

rwa_download_files(file_list = capture_2021, 
                   directory = "purple-lake", 
                   bucket_name = "purple-lake-poissonconsulting")
```

## How to Contribute

Please report any [issues](https://github.com/poissonconsulting/readwriteaws/issues).

[Pull requests](https://github.com/poissonconsulting/readwriteaws/pulls) are always welcome.

Please note that the readwriteaws project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
